Digital Analysis of Paintings

### 2014-05-10 paper.tex
Preliminary finish.
Everything is done, bib is balanced as per IEEE style reccomendations. Could do
with a read through though.

\begin{abstract}
%TODO Write this once the paper is complete
\end{abstract}

% no keywords

@@

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

>>>>

\begin{abstract}
%TODO Write this once the paper is complete
The recent trend in the digitisation of historic artwork has opened up a whole
field of digital image processing. The digital analysis of paintings can be
used to perform numerous tasks, from detecting forgeries to the animation of
still life works. This work will review some of the research which has been
performed into this area to provide a starting point for any future research.
\end{abstract}

@@

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
\IEEEtriggeratref{17}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}
